The IFC system uses a MSP430F5529 as a Microcontroller Unit (MCU). The MSP430F5529 is a mixed signal MCU uses for low-power applications. It features a 1.8V to 3.6V power-supply, a 16-bit RISC CPU, a 25MHz maximum Master Clock (MCLK) powered by a digital Frequency-Locked Loop (FLL) powered by a low frequency 32kHz watch crystal, 12-bit ADCs, 63 I/O pins, a 3-channel DMA with an extended memory, 16-bit timers, timers, interrupts, comparators, 5 different Low-Power Modes (LPM). It supports communication with UART, enhanced UART, SPI, I2C, IrDA, USB 2.0, and is programmed/debuggued by JTAG. It dissipates about 6 mW when active and 24 $\mu$W when in LPM. \par

The impedance-sensing system uses:
\begin{itemize}
	\item 6 channels of the 12-bit ADCs to measure: $\Re(V_{PSD-\omega_0})$ and $\Im(V_{PSD-\omega_0})$ of the two electrode responses, the 5V $V_{DD}$ power-supply, and the battery voltage. 
	\item A 32-kHz watch crystal creates a MCLK oscillating at 16MHz with the PLL. 
	\item The I2C module used to program the Si5351 and modify the excitation signal frequency. 
	\item The UART module used with the external IC FT232RL to convert the sampled data to RS232 to be transfered to a nearby computer.
	\item A couple of I/O pins to enable the power-supplies, monitor the status of the system by activating LEDs, modify the gains of the PGA on the fly, modify the phase of the measurement by enabling or disabling the flip-flops of the quadrature generator, and reset the MCU at the press of a button. 
\end{itemize}